Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-03-19 paper.tex
Fix ref

In this study we seek to predict the near-wake of the UNH-RVAT turbine, shown in
Figure~\ref{fig:RVAT-CAD}. Experimental performance curves for the UNH-RVAT are
shown in Figure~\ref{fig:exp_perf}. We modeled the turbine at a tip speed ratio
$\lambda=1.9$, which corresponds to the maximum power coefficient, and a turbine
diameter Reynolds number $Re_D \approx 10^6$, which corresponds to a
$Re$-independent state for both performance and near-wake characteristics, as
determined from experimental measurements \cite{Bachant2014,
    Bachant2015-RVAT-Re-dep}.

>>>>

In this study we seek to predict the near-wake of the UNH-RVAT turbine, shown in
Figure~\ref{fig:RVAT-CAD}. Experimental performance curves for the UNH-RVAT are
shown in Figure~\ref{fig:exp_perf}. We modeled the turbine at a tip speed ratio
$\lambda=1.9$, which corresponds to the maximum power coefficient, and a turbine
diameter Reynolds number $Re_D \approx 10^6$, which corresponds to a
$Re$-independent state for both performance and near-wake characteristics, as
determined from experimental measurements \cite{Bachant2014,
    Bachant2016-RVAT-Re-dep}.
